1. Read the "train.csv" file from the following website.
"https://raw.githubusercontent.com/agconti/kaggle-titanic/master/data/train.csv"
```{r echo=TRUE}
data<-read.csv(file="https://raw.githubusercontent.com/agconti/kaggle-titanic/master/data/train.csv",header=T,sep=",")
```

View(train.data)

2. Have a look at the data set.
```{r echo=TRUE}
head(data)
tail(data)
str(data)
```

3. SInce we see thriuth the structure the Pclass and Survived listed as an integer. So here we are in need to Change the "Pclass" 
and "Survived" attributes to factors.
```{r echo=TRUE}
data$Pclass = factor(data$Pclass)
data$Survived = factor(data$Survived)
str(data)
```

4. Check the missing values of the "Age" and "Name" attributes. 
```{r echo=TRUE}
sum(is.na(data$Age))
length(data$Age)
sum(is.na(data$Name))
length(data$Name)
```

5. For a title containing a missing value, assign the mean age value for each title not containing a missing value. 
(Hint: grepl(" Mr\\.", train.data$Name))
```{r echo=TRUE}
mean.mr = mean(data$Age[grepl(" Mr\\.",
     data$Name) & !is.na(data$Age)])
data$Age[grepl(" Mr\\.",data$Name) & is.na(data$Age)]=mean.mr
mean.mr
```

```{r echo=TRUE}
mean.mrs = mean(data$Age[grepl(" Mrs\\.", 
      data$Name) & !is.na(data$Age)])
data$Age[grepl(" Mrs\\.",data$Name)&is.na(data$Age)]=mean.mrs
mean.mrs
```
```{r echo=TRUE}
mean.dr = mean(data$Age[grepl(" Dr\\.",
      data$Name) & !is.na(data$Age)])
data$Age[grepl(" Dr\\.",data$Name) & is.na(data$Age)]=mean.dr
mean.dr
```
```{r echo=TRUE}
mean.miss = mean(data$Age[grepl(" Miss\\.", 
      data$Name) & !is.na(data$Age)])
data$Age[grepl(" Miss\\.",data$Name) & is.na(data$Age)]=mean.miss
mean.miss
```
```{r echo=TRUE}
mean.master = mean(data$Age[grepl(" Master\\.",
       data$Name) & !is.na(data$Age)])
data$Age[grepl(" Master\\.", data$Name) & is.na(data$Age)]=mean.master
mean.master
```

View(data)

6. List the distribution of Port of Embarkation. Replace empty entries with NA for "Embarked" attribute.
```{r echo=TRUE}
str(data$Embarked)
table(data$Embarked, useNA = "always")
data$Embarked<-replace(data$Embarked,data$Embarked == "", NA)
sum(is.na(data$Embarked))
```

7. Assign the two missing values to the most counted port, which is Southampton in this case.
```{r echo=TRUE}
data$Embarked[which(is.na(data$Embarked))] = 'S'
table(data$Embarked, useNA = "always")
str(data$Embarked)

table_ <- table(data$Embarked, useNA = "always")

which.max(table_)
```

