#Setting the working diectory and establishing a connection to MYSQL Server
```{r}
install.packages('RMySQL', dependencies = TRUE)
library(RMySQL)
sqlQuery <- function (query) {

  # creating DB connection object with RMysql package
  # Please consider changing the username and password 
  DB <- dbConnect(MySQL(), user='root', password='data', dbname='LibraryDB',
        host='127.0.0.1')
  
  # send Query to btain result set
  rs <- dbSendQuery(DB, query)

  # get elements from result sets and convert to dataframe
  result <- fetch(rs, -1)
  
  # close db connection after function call exits
  on.exit(dbDisconnect(DB))

  # return the dataframe
  return(result)
}
```

#Example 1
Retrieve the name and address of all borrowers.
```{r}
sqlQuery("SELECT name, address FROM borrower;")
```

##Q1
Add columns 'EmailAddr' and 'PhoneNo' in sequence to Table 'Borrower'
```{r}
sqlQuery("ALTER TABLE borrower 
         ADD COLUMN EmailAddr VARCHAR(255), ADD COLUMN PhoneNo INT(10);");
```

##Q2
a) Add column 'Charge' to Table 'Borrower' using data type "FLOAT". 
b) Drop the column.
c) Add the column again using data type "Decimal(5,2)".
```{r}
sqlQuery("ALTER TABLE borrower 
         ADD COLUMN Charge FLOAT;") 
sqlQuery("ALTER TABLE borrower 
         DROP COLUMN Charge;")
sqlQuery("ALTER TABLE borrower 
         ADD COLUMN Charge Decimal(5,2);")
```

##Q3
For library card numbers 1667, 7032 and 9781, change 'charge' values to 1.50.
```{r}
sqlQuery("UPDATE borrower 
         SET Charge = 1.50
         WHERE LibraryCardNo IN (1667, 7032, 9781);")
```

##Q4
Change column name from 'Charge' to 'ChargeNew' with a default value of 0.00
```{r}
sqlQuery("ALTER TABLE borrower 
         CHANGE COLUMN Charge ChargeNew Decimal(5,2) DEFAULT 0.00;")
```

##Q5
For library card numbers 5007 and 8163, change the charge values to 0.00
```{r}
sqlQuery("UPDATE borrower 
         SET ChargeNew = 0.00 WHERE LibraryCardNo IN (5007, 8163);")
```

##Q6
Create a new Table called 'BorrowerCharge' through selecting 'LibraryCardNo' and 'ChargeNew' from Table 'Borrower'.
```{r}
sqlQuery("CREATE TABLE BorrowerCharge AS
         SELECT LibraryCardNo, ChargeNew
         FROM borrower;")
```

##Q7
From Table 'BorrowerCharge', remove all rows where library card number equals to 8163
```{r}
sqlQuery("DELETE FROM BorrowerCharge WHERE LibraryCardNo = 8163;")
```

##Q8
Add foreign key constraints to 'BookNo' in Table 'BookLended', referencing 'BookNo' in Table 'Book' and 'librarycardno' in Table 'Borrower'
```{r}
sqlQuery("ALTER TABLE bookLended 
         ADD CONSTRAINT LibraryCardNo FOREIGN KEY (LibraryCardNo) 
         REFERENCES borrower(LibraryCardNo), 
         ADD CONSTRAINT BookId FOREIGN KEY (BookId) REFERENCES books(BookNo);")
```

##Q9
Retrieve the names and charges from Borrowers whose charges are greater than 0
```{r}
sqlQuery("SELECT name, ChargeNew FROM borrower
         WHERE ChargeNew > 0;")
```

##Q10
Find the average of the charges of all borrowers.
```{r}
sqlQuery("SELECT AVG(ChargeNew) AS Average_Charges 
         FROM borrower;")
```

##Q11
Retrieve the names and authors of the books that make at least $50 more than the book which costs the least.
```{r}
sqlQuery("SELECT Title, Author FROM books 
         WHERE Cost >= (SELECT  min(Cost) FROM books) + 50;")
```

##Q12
Find all the information about Borrowers who have borrowed a book.
```{r}
sqlQuery("SELECT * FROM borrower NATURAL JOIN bookLended;")
```

##Q13
Create a virtual table to view borrowers' information using library card number, charges, address, check-out date, return date, book number, copyid and librarian columns.
```{r}
sqlQuery("CREATE VIEW borrowerI AS
         SELECT A.LibraryCardNo, A.ChargeNew, A.Address,
         B.CheckOutDate, B.ReturnDate, B.BookId, B.CopyId, B.Librarian FROM borrower A, bookLended B
         WHERE A.LibraryCardNo = B.LibraryCardNo;")
sqlQuery("SELECT * FROM borrowerI;")
```

##Q14
Retrieve library card numbers from Table 'LibraryCardNo' and Table 'BookLended' and combine them together (duplicate values also) in a row-wise manner
```{r}
sqlQuery("SELECT LibraryCardNo FROM borrower 
         UNION ALL SELECT LibraryCardNo FROM bookLended 
         ORDER BY LibraryCardNo;")
```

##Q15
Count the number of librarians grouped by library card number in Table 'BookLended'.
```{r}
sqlQuery("SELECT count(DISTINCT LibraryCardNo) FROM bookLended;")
```
